This is an example of article title

### 2025-10-28 paper/paper.tex
first csv export.
Finish a first draft of the Bézier example.

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{amsmath,booktabs,mathtools,amssymb}
\newcommand{\term}[1]{\emph{#1}}
\newcommand{\e}{\ensuremath{\mathrm{e}}}
\newcommand{\im}{\ensuremath{\mathrm{i}}}
\newcommand{\LieGroupsVersion}{0.1.6}
%
\hypersetup{colorlinks=true}
%
\begin{document}

@@

In Algorithm~\ref{lst:deCasteljauLieGroup}, define the general de-Casteljau algorithm on a Lie group \verb|G|, given a vector of control points \verb|cp| and a parameter \verb|t| in \([0,1]\).

We can now compare the algorithm on the Lie group \(\mathrm{SE}(2)\) with the corresponding Bézier curve on the (direct) product Lie group $\mathrm{SO}(2) \times \mathbb{R}^2$. Denote by $R_\alpha$ the rotation matrix in \(\mathrm{SO}(2)\) for an angle \(\alpha\in[0,2\pi)\). Then we consider the control points
\begin{align*}
    g_1 &= \begin{pmatrix} R_0 & \begin{pmatrix} 0 \\ 0 \end{pmatrix} \\
    0 & 1 \end{pmatrix}, \quad
g_2 = \begin{pmatrix} R_{\pi/2} & \begin{pmatrix} 1 \\ 0 \end{pmatrix} \\
    0 & 1 \end{pmatrix}, \\
g_3 &= \begin{pmatrix} R_{\pi} & \begin{pmatrix}
    1 \\ 1 \end{pmatrix} \\
0 & 1 \end{pmatrix}, \quad
\end{align*}

As data we take the points

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{amsmath,booktabs,mathtools,amssymb}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.18}

\newcommand{\term}[1]{\emph{#1}}
\newcommand{\e}{\ensuremath{\mathrm{e}}}
\newcommand{\im}{\ensuremath{\mathrm{i}}}
\newcommand{\LieGroupsVersion}{0.1.6}
%
% Define muted colors.
\definecolor{TolMutedBlue}{HTML}{332288}
\definecolor{TolMutedCyan}{HTML}{88CCEE}
\definecolor{TolMutedTeal}{HTML}{44AA99}
\definecolor{TolMutedGreen}{HTML}{117733}
\definecolor{TolMutedOlive}{HTML}{999933}
\definecolor{TolMutedSand}{HTML}{DDCC77}
\definecolor{TolMutedRose}{HTML}{CC6677}
\definecolor{TolMutedWine}{HTML}{882255}
\definecolor{TolMutedPurple}{HTML}{AA4499}
%
\hypersetup{colorlinks=true}
%
\begin{document}

@@

In Code~\ref{lst:deCasteljauLieGroup}, we define the general de-Casteljau algorithm on a Lie group \verb|G|, given a vector of control points \verb|cp| and a parameter \verb|t| in \([0,1]\).

We can now compare the algorithm on the Lie group \(\mathrm{SE}(2)\) with the corresponding Bézier curve on the (direct) product Lie group $\mathrm{SO}(2) \times \mathcal T(2)$, where \(\mathcal T(2) = (\mathbb{R}^2, +)\) is the \verb|TranslationGroup(2)|.
Denote by $R_\alpha$ the rotation matrix in \(\mathrm{SO}(2)\) for an angle \(\alpha\in[0,2\pi)\).
We consider the control points
\begin{align*}
    g_1 &= \Bigl(R_{\frac{\pi}{2}}, \begin{pmatrix} 0 \\ 0 \end{pmatrix}\Bigr),
    &\quad
    g_2 &= \Bigl(R_{\frac{\pi}{4}}, \begin{pmatrix} 1/3 \\ 1/2 \end{pmatrix}\Bigr),
    \\%\quad
    g_3 &= \Bigl(R_{\frac{3\pi}{4}}, \begin{pmatrix} 2/3 \\ -1/2 \end{pmatrix}\Bigr),
    &\quad
    g_4 &= \Bigl(R_{\pi}, \begin{pmatrix} 1 \\ 0 \end{pmatrix}\Bigr).
\end{align*}

We evaluate the corresponding Bézier curves on both Lie groups using the code in~\ref{lst:bezierLieGroupExample}.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:bezierLieGroupExample},
    caption={Evaluating Bézier curves on \(\mathrm{SE}(2)\) and \(\mathrm{SO}(2) \times \mathcal T(2)\).}
]
ts = range(0, 1, length=35)
q1 = [
    deCasteljauLieGroup(SO2xT2, cp, t) for t in ts
]
q2 = [deCasteljauLieGroup(SE2, cp, t) for t in ts]
\end{lstlisting}

\begin{figure}
    % Arrow scale factor
    \def\arrowscale{0.15}

    \begin{tikzpicture}
        \begin{axis}[
            grid=major,
            width=.5\textwidth,
            legend style={at={(0.95,0.9)}},
            xmin=-0.05, xmax=1.05,
            ymin=-0.525, ymax=0.625,
            unit vector ratio=1 1,
            title style={yshift=-.5\baselineskip,},
            title={Two Bézier curves on different Lie groups},
        ]
            % Control points
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, very thick, TolMutedBlue,
            ] table[col sep=comma] {data/bezier_example_control_points.csv};
            \addlegendentry{Control points}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=2pt, TolMutedBlue, forget plot,
                ] table[col sep=comma] {data/bezier_example_control_points.csv};
            % SO2xR2 Curve and quiver
            \addplot[solid, thick, TolMutedSand, forget plot] table[col sep=comma, x=x, y=y] {data/bezier_example_so2r2_dense_curve.csv};
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, TolMutedSand,
            ] table[col sep=comma] {data/bezier_example_so2r2.csv};
            \addlegendentry{$\mathrm{SO}(2)\times \mathcal T(2)$}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=1.5pt, TolMutedSand, forget plot,
                ] table[col sep=comma] {data/bezier_example_so2r2.csv};
            % SE2 Curve and quiver
            \addplot[solid, thick, TolMutedTeal, forget plot] table[col sep=comma, x=x, y=y] {data/bezier_example_se2_dense_curve.csv};
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, TolMutedTeal,
            ] table[col sep=comma] {data/bezier_example_se2.csv};
            \addlegendentry{$\mathrm{SE}(2)$}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=1.5pt, TolMutedTeal, forget plot,
                ] table[col sep=comma] {data/bezier_example_se2.csv};
        \end{axis}
    \end{tikzpicture}
    \caption{Bézier curves on the Lie groups \(\mathrm{SE}(2)\) (teal) and \(\mathrm{SO}(2) \times \mathbb{R}^2\) (sand) based on the same control points
    $g_1,\ldots,g_4$ (blue).}
\end{figure}
